babette: BEAUti 2, BEAST2 and Tracer for R

### 2018-02-09 article.tex
Better

  \textbf{1. }
    In the field of phylogenetics, 
     BEAST2 is one of the most widely used software tools. 
     It comes with the graphical programs BEAUti 2 to
     facilitate the creation of input files to BEAST2, and
     with DensiTree and Tracer, 
     to interpret BEAST2's output. 
     However, when many input files are required, 
     a workflow of GUI programs is cumbersome. 
     Moreover, many other phygenetics tools are available 
     in R, which requires switching from one platform 
     to the other. \\
  \textbf{2. }
    Here, we present a free, libre and open-source package, \verb;babette;, 
    'BEAUti 2, BEAST2 and Tracer for R', for the R programming language. 
    \verb;babette; creates BEAST2 input files, runs BEAST2 and parses its results, 
    from an R function call. \\
  \textbf{3. }
    We describe \verb;babette;'s usage, the novel functionality it provides
    compared to the tools it replaces, and give some examples. \\
  \textbf{4. }
    As \verb;babette; is designed to be of high quality and extendable, 
    we conclude by describing the further development of the package \\
\end{abstract}

>>>>

  \textbf{1. }
    In the field of phylogenetics, 
     BEAST2 is one of the most widely used software tools. 
     It comes with the graphical programs BEAUti 2 to
     facilitate the creation of BEAST2 configuration files, and
     with DensiTree and Tracer, to interpret BEAST2's output files. 
     However, when many different alignments or model 
     setups are required, a workflow of GUI programs is cumbersome. \\
  \textbf{2. }
    Here, we present a free, libre and open-source package, \verb;babette;, 
    'BEAUti 2, BEAST2 and Tracer for R', for the R programming language. 
    \verb;babette; creates BEAST2 input files, runs BEAST2 and parses its results, 
    all from an R function call. \\
  \textbf{3. }
    We describe \verb;babette;'s usage, the novel functionality it provides
    compared to the tools it is alternative of, and give some examples. \\
  \textbf{4. }
    As \verb;babette; is designed to be of high quality and extendable, 
    we conclude by describing the further development of the package \\
\end{abstract}
